Tropical Andes Taxonomic Diversity of Plants and Frugivores

### 2024-05-16 code/L2/L2_1_TropicalAndes_taxdiv.Rmd
fine tunning multipannel plot for maps

# Multi panel plots
Richness maps
```{r}
all_richness_plots <- ggpubr::ggarrange(#plantgridRichTA_1km, plantgridRichTA_5km, 
                                              #plantgridRichTA_10km, 
                                              plantgridRichTA_25km,
                                              plantgridRichTA_50km, plantgridRichTA_75km,
                                              plantgridRichTA_100km,
                                              #frugivoregridRichTA_1km, frugivoregridRichTA_5km, 
                                              #frugivoregridRichTA_10km, 
                                              frugivoregridRichTA_25km,
                                              frugivoregridRichTA_50km, frugivoregridRichTA_75km,
                                              frugivoregridRichTA_100km, 
                                              ncol = 4, nrow = 2)
all_richness_plots
ggsave("all_richness_plots.png", all_richness_plots, path = output_path, width = 20, height = 8.5, units = "in")
```

>>>>

# Multi panel plots
## Richness maps
```{r}
all_plant_richness_plots <- ggpubr::ggarrange(#plantgridRichTA_1km, plantgridRichTA_5km, 
                                              #plantgridRichTA_10km, 
                                              plantgridRichTA_25km,
                                              plantgridRichTA_50km, plantgridRichTA_75km,
                                              plantgridRichTA_100km,
                                              ncol = 4, nrow = 1,
                                              labels = c("25 km", "50 km", "75 km", "100 km"),
                                              common.legend = TRUE, legend = "right")
all_plant_richness_plots_labeled <- ggpubr::annotate_figure(all_plant_richness_plots,
                                                            left = ggpubr::text_grob("Plants", face = "bold", size = 14))
all_plant_richness_plots_labeled
```

```{r}
all_frugivore_richness_plots <- ggpubr::ggarrange(#frugivoregridRichTA_1km, frugivoregridRichTA_5km, 
                                              #frugivoregridRichTA_10km, 
                                              frugivoregridRichTA_25km,
                                              frugivoregridRichTA_50km, frugivoregridRichTA_75km,
                                              frugivoregridRichTA_100km,
                                              ncol = 4, nrow = 1,
                                              labels = c("25 km", "50 km", "75 km", "100 km"),
                                              common.legend = TRUE, legend = "right")
all_frugivore_richness_plots_labeled <- ggpubr::annotate_figure(all_frugivore_richness_plots,
                                                            left = ggpubr::text_grob("Frugivores", face = "bold", size = 14))
all_frugivore_richness_plots_labeled
```

```{r}
all_richness_plots <- ggpubr::ggarrange(all_plant_richness_plots_labeled,
                                        all_frugivore_richness_plots_labeled,
                                        ncol = 1, nrow = 2)
all_richness_plots
ggsave("all_richness_plots.png", all_richness_plots, path = figure_path, width = 11, height = 8, units = "in")
```
